---
title: "jah667_Lab1_1272023"
author: "Jessie"
date: "2023-01-27"
output: 
  html_document: 
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What...is your name?

## What...is your favorite color?

<br> This is a pagebreak function

### What...is the average velocity of a coconut-laden swallow?

*It depends on whether we're talking about an African swallow or a European swallow*
<br>

**Implementing R code into your markdown file:**
<br>
The answer to 2+2 is `r 2+2`!
<br>

**Can also implement datasets from R into RMarkdown**
 <br>
The number of rows in the "cars" dataset built into R is `r nrow(cars)`
<br>

Monty Python is a cultural masterpiece:
<br>
<br>

<center> Centered Text look at us go (this text is centered using HTML!)</center>
<br> 

Now let's work on adding more R into this text and different ways to do it
<br>
<br>
Echo is the command that allows you to continue an R string within a document. This continuation of a string is called a chunk.
```{r, echo=FALSE, eval=TRUE} 
nrow(cars)
ncol(cars)

plot(cars$speed, cars$dist)
```
<br>
To end the chunk, use the little dots like this ` 
<br>

This is a footnote^[this is the footnote!]